A Review on Multi-Label Learning Algorithms

### 2018-01-15 Paper/Presentation/mll_review.tex
update presentation with related work

\section{Introduction} % Sections can be created in order to organize your presentation into discrete blocks, all sections and subsections are automatically printed in the table of contents as an overview of the talk
\subsection{Problem Definition}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
Single-label supervised learning
\begin{itemize}
	\item Applied to classification
	\item Supervised: Dataset $\{ (x_i, y_i)\}, i = 1, \dots N, x \in X, y \in Y$
	\item Goal is to learn a model $f: X \rightarrow Y$
\end{itemize}

@@

\end{itemize}
TODO: Include stuff about multi-labeled dataset characterization?
\end{frame}

%------------------------------------------------
\subsection{Algorithm Strategies}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
Label search space $\mathbb{S_Y}$ grows exponentially as a function of $|Y|=q$
\begin{itemize}
	\item e.g. for $q=20, |\mathbb{S_Y}| = 2 ^ {|\mathbb{P(Y)}|} = 2^{20} \ge 10^6$
\end{itemize}
Solution: integrate in the learning process potential label correlations.
This work examines algorithms grouped in three broad categories:

@@

%------------------------------------------------
\subsection{Evaluation Metrics}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
Two categories and perspectives:
	\begin{itemize}
		\item \emph{Example-based: }Evaluates multi-labelled performance on each example, extrapolate to whole dataset
		\begin{itemize}
			\item \emph{Classification perspective:} 
				\begin{itemize}
					\item Subset Accuracy, Hamming Loss
					\item Precision, Recall, F-measure, F$^\beta$ -measure
				\end{itemize}
			\item \emph{Ranking perspective:} one-error, coverage, ranking loss, average precision
		\end{itemize}
		\item \emph{Label-based: }Evaluates performance on each label separately, extrapolate to whole label set
		\begin{itemize}
			\item Classification perspective: Macro/Micro averaging for single-label example-based, classification-based measures
			\item Ranking perspective: Macro/Micro averaging for AUC 
		\end{itemize}
	\end{itemize}
	Classifiers should aim to optimize \emph{multiple} metrics
\end{frame}
%------------------------------------------------
\section{Multi-label Learning Algorithms}
%------------------------------------------------

\subsection{Categorization}

\begin{frame}
\frametitle{\insertsection : \insertsubsection}

@@

Future goals:
\begin{itemize}
	\item Holy grail: Formal characterization on the underlying concept / mechanism on the appropriate usage of label correlations, especially on large output spaces
	\item Thorough experimental comparative study to discover to pros and cons of different multi-label learning algorithms
\end{itemize}
\end{frame}

>>>>

\section{Introduction} % Sections can be created in order to organize your presentation into discrete blocks, all sections and subsections are automatically printed in the table of contents as an overview of the talk
\subsection{Problem Definition}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Introduction}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
Single-label supervised learning
\begin{itemize}
\item Applied to classification
\item Supervised: Dataset $\{ (x_i, y_i)\}, i = 1, \dots N, x \in X, y \in Y$
\item Goal is to learn a model $f: X \rightarrow Y$
\end{itemize}

@@

\end{itemize}
TODO: Include stuff about multi-labeled dataset characterization?
\end{frame}
%------------------------------------------------
\subsection{Related Work}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{itemize}
\item Madjarov, Gjorgji, et al. "An extensive experimental comparison of methods for multi-label learning." Pattern Recognition 45.9 (2012): 3084-3104
\item Tsoumakas, Grigorios, and Ioannis Katakis. "Multi-label classification: An overview." International Journal of Data Warehousing and Mining 3.3 (2006)
\item Zhang, Min-Ling, and Kun Zhang. "Multi-label learning by exploiting label dependency." Proceedings of the 16th ACM SIGKDD international conference on Knowledge discovery and data mining. ACM, 2010
\end{itemize}
\end{frame}
%------------------------------------------------
\subsection{Algorithm Strategies}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
Label search space $\mathbb{S_Y}$ grows exponentially as a function of $|Y|=q$
\begin{itemize}
\item e.g. for $q=20, |\mathbb{S_Y}| = 2 ^ {|\mathbb{P(Y)}|} = 2^{20} \ge 10^6$
\end{itemize}
Solution: integrate in the learning process potential label correlations.
This work examines algorithms grouped in three broad categories:

@@

%------------------------------------------------
\subsection{Evaluation Metrics}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
Two categories and perspectives:
\begin{itemize}
\item \emph{Example-based: }Evaluates multi-labelled performance on each example, extrapolate to whole dataset
\begin{itemize}
\item \emph{Classification perspective:}
\begin{itemize}
\item Subset Accuracy, Hamming Loss
\item Precision, Recall, F-measure, F$^\beta$ -measure
\end{itemize}
\item \emph{Ranking perspective:} one-error, coverage, ranking loss, average precision
\end{itemize}
\item \emph{Label-based: }Evaluates performance on each label separately, extrapolate to whole label set
\begin{itemize}
\item Classification perspective: Macro/Micro averaging for single-label example-based, classification-based measures
\item Ranking perspective: Macro/Micro averaging for AUC
\end{itemize}
\end{itemize}
Classifiers should aim to optimize \emph{multiple} metrics
\end{frame}
%------------------------------------------------
\section{Multi-label Learning Algorithms}
%------------------------------------------------
\subsection{Categorization}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Multi-label Learning Algorithms}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : \insertsubsection}

@@

Future goals:
\begin{itemize}
\item Holy grail: Formal characterization on the underlying concept / mechanism on the appropriate usage of label correlations, especially on large output spaces
\item Thorough experimental comparative study to discover pros and cons of different multi-label learning algorithms
\end{itemize}
\end{frame}
